Milestone 2: Datasets Generation

### 2019-10-21 perf_release_criteria/milestone_3/ms_2_dataset_generation.Rmd
Creating new `milestone 3` directory for analysis.

```{r imports, echo=FALSE, warning=FALSE, message=FALSE}
source('lib/supporting_funcs.R')
```

# tl;dr 
This notebook generates the training and validation datasets used to determine the model framework for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee). These datasets will be used for all steps in the process detailed out in the [document](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.nwwrif453n80).

@@

* `na.omit` is not applied.
* OS is filtered to only Windows.

@@

df_train <- load_df('data/milestone2/df_pd_67.csv')
df_validate <- load_df('data/milestone2/df_pd_68.csv')
```

@@

# Serialize and push to GCP
Save the result dataset to an R image.

```{r serialize}
image_file_path <- paste('data/milestone2/df_train_validate_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
save(df_train_f, df_validate_f, file = image_file_path)
```

The push the results to GCP in the `moz-fx-dev-subbeta` bucket, under `r image_file_path`.

>>>>

```{r imports, echo=FALSE, warning=FALSE, message=FALSE}
source('../lib/supporting_funcs.R')
```

# tl;dr 
This notebook generates the training and validation datasets used to determine the model framework for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee). These datasets will be used for all steps in the process detailed out in the [document](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.nwwrif453n80). In addition, the bootstrap replicates for feature selection and hyperparameter tuning are created. These datasets are all stored in GCP under the `moz-fx-dev-cdowhyglund-subBeta` project.

@@

* `na.omit` is not applied.
* Missing values are only dropped for the performance metrics (outcomes) of concern
* OS is filtered to only Windows.

@@

df_train <- load_df('../data/milestone2/df_pd_67.csv')
df_validate <- load_df('../data/milestone2/df_pd_68.csv')
```

@@

# Bootstrap Samples

```{r balancing, echo=FALSE}
channel_counts <- df_train_f %>% count(label)
release_overcount <- channel_counts$n[channel_counts$label == 'release'] - channel_counts$n[channel_counts$label == 'beta']
```

The feature selection will utilize 10 boostrap replicates, which are generated as follows:
1. The entire `df_train` dataset is sampled at 100% with replacement.
2. A sample of Release (`is_release = TRUE`) `client_id` are taken of the same size as Beta (`r channel_counts$n[channel_counts$label == 'beta']`)
3. The entire (resampled) Beta `client_id` are combined with this sampled Release ids. 
    - These are the profiles that will be used for building the matching model. 
    - The matched Beta profiles will be used for scoring the model. 
4. The remaining Release ids will be used for scoring the model.

The same set of bootstrap samples will be used for all feature selection across modeling algorithms. A suite of these are created to represent different levels of Beta oversampling with respect to Release.

```{r bootstrap_def}
extract_ids <- function(df_c, size, oversampling){
  df_beta <- df_c %>% filter(is_release == FALSE)
  df_rel <- df_c %>% filter(is_release == TRUE)
  n_beta <- nrow(df_beta)

  model_ids <- df_rel %>%
    sample_n(size = round(n_beta / oversampling)) %>%
    rbind(df_beta) %>%
    pull(client_id)

  # create the dataset for scoring matching model
  test_ids <- df_rel %>% 
    filter(!client_id %in% model_ids) %>%
    pull(client_id)

  return(list(train = model_ids, test = test_ids))
}

gen_bootstraps <- function(df_train, oversampling = 1, num_bts = 10){
  bts <- list()
  for (i in 1:num_bts){
    # create a resampled version of entire dataframe
    df_resampled <- df_train %>% sample_frac(replace = TRUE)
    # create train/test "splits"
    bts[[i]] <- extract_ids(df_resampled, oversampling = oversampling)
  }
  return(bts)
}
```

```{r bootstrap_gen}
bts.1x <- gen_bootstraps(df_train_f)
bts.4x <- gen_bootstraps(df_train_f, oversampling = 4)
bts.8x <- gen_bootstraps(df_train_f, oversampling = 8)
bts.16x <- gen_bootstraps(df_train_f, oversampling = 16)
```

# Serialize and push to GCP
Save the resultant dataset and bootstrap samples to an R image.

```{r serialize_dataset}
image_file_path <- paste('data/milestone2/df_train_validate_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
save(df_train_f, df_validate_f, bts.1x, bts.4x, bts.8x, bts.16x,
     file = image_file_path)
```

Then push the results to GCP in the `moz-fx-dev-subbeta` bucket, under `r image_file_path`.
